### 2021-04-17 README.Rmd
Actually got the vignettes to work this time, with the windows check too I think

## Citations

- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
- If you use `{mshap}`, please cite [this article](https://google.com)

>>>>

## Attribution

- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
- If you use `{mshap}`, please cite [this article](https://www.google.com/)
